Increasing the mortality gap? Social inequality in mortality among elderly and adults in Northern Sweden 1851--2013\footnote{Session "Health, morbidity, and mortality" at the Nordic Demographic Symposium 14--16 June 2017, Turku, Finland}

### 2017-10-06 cape.Rnw
improve a figure

<<setup, include = FALSE>>=
library(knitr)
opts_chunk$set(engine='R',dev='pdf',fig.path='figs/ume-',tidy=FALSE,fig.height=5.5,fig.width=8,strip.white=TRUE,cache=TRUE,echo=FALSE,message=FALSE,comment=NA,show.signif.stars = FALSE)##$
@

<<environ>>=
library(knitr)
library(eha)
library(xtable)
library(skum)
@

@@

<<cumsw>>=
source("R/plotED.glm.R")
scol <- c("blue", "darkgreen", "red", "black")
oldpar <- par(mfrow = c(2, 1), cex = 0.7, lwd = 1.5)
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Women 40-64", exclude = 5:6)
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Men 40-64")##, exclude = 5:6)
par(oldpar)
@

@@

>>>>

<<setup, include = FALSE>>=
library(knitr)
opts_chunk$set(engine='R',dev='pdf',fig.path='figs/ume-',tidy=FALSE,fig.height=5.5,fig.width=8,strip.white=TRUE,cache=FALSE,echo=FALSE,message=FALSE,comment=NA,show.signif.stars = FALSE)##$
@

<<environ>>=n
library(knitr)
library(eha)
library(xtable)
library(skum)
@

@@

<<cumsw>>=
source("R/plotED.glm.R")
scol <- c("blue", "darkgreen", "darkgreen", "red")
oldpar <- par(mfrow = c(2, 1), cex = 0.7, lwd = 1.5)
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Women 40-64")## exclude = 5:6)
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Men 40-64")##, exclude = 5:6)
par(oldpar)
@

\begin{frame}{Women and men, age 40--64, 1976--2013}

<<cumswlate>>=
source("R/plotED.glm.R")
oldpar <- par(mfrow = c(2, 1), cex = 0.7, lwd = 1.5)
woutp <- plotED.glm(resw, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Women 40-64", exclude = 1:6)
moutp <- plotED.glm(resm, col = scol, logScale = FALSE, ylab = "TMR(65|40)",
                main = "Men 40-64", exclude = 1:6)
par(oldpar)
@

@@

\begin{frame}{Relative differences, ages 40--64}

  %\begin{center}
\includegraphics[height=7.5cm,width=10.8cm]{figs/art2-cumswstand-1}
   %\end{center}
\end{frame}

\begin{frame}{Relative differences, ages 65--89}

  %\begin{center}
\includegraphics[height=7.5cm,width=10.8cm]{figs/art2-cumswold-1}
   %\end{center}
\end{frame}
